---
title: ""
author: ""
date: ""
output:
  html_document:
    keep_md: true
  md_document:
    variant: markdown_github
---

`threatcrowd` an R pacakge to work with the [ThreatCrowd](https://github.com/threatcrowd/ApiV2) API

The following functions are implemented:

- `search_avs`:	Search anti-virus indicators
- `search_domains`:	Search domain indicators
- `search_email`:	Search e-mail indicators
- `search_ips`:	Search IP indicators

<hr/>
NOTE: This requries `httr` >=1.0 (which should be in CRAN soon if not already there)
<hr/>

### News

- Version 0.1.0.9000 initial release

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/threatcrowd")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(threatcrowd)

# current verison
packageVersion("threatcrowd")

search_email("william19770319@yahoo.com")

search_domains("aoldaily.com")

search_ips("188.40.75.132")

search_avs("plugx")

```

### Test Results

```{r}
library(threatcrowd)
library(testthat)

date()

test_dir("tests/")
```

